The Prevalence of E-Mail Header Injections on the World Wide Web

### 2016-05-24 System/proof_of_concept.tex
Edited through the results section
fixed all todos in exp_setup

The front-end for each of the three applications is shown in Listing~\ref{code:html}. The server-side code for the PHP and Python is shown in Listings~\ref{code:phpemi} and \ref{code:pyemi} respectively.

% Adam: I think it might be nice to have the Ruby code here too.

Before performing out wide scan of the web, we verified that our system was able to detect the \ehi vulnerabilities present in all the sample web applications.

@@

\begin{lstlisting}[language=HTML,caption={HTML page for showcasing
      \ehi, a simple front-end for our
      examples.},label={code:html}, float]
<!doctype html>
<html lang="en">
<head>
<meta charset="utf-8">
<meta name="author" content="XYZ">
<title>Mock Email</title>
</head>
<body>
<form action="{path-to-back-end}" method="post">
<input type="text" placeholder="Email" name="email" id="\email"><br>
<textarea name="msg" rows="20" cols="120"></textarea>
<input type="submit" value="Email Me!">
</form>
</body>
</html>
\end{lstlisting}

%% \begin{figure}[!htbp]
%% 	\centering
%% 	\includegraphics[width=\linewidth]{System/EMI_Postman_Ruby}
%% 	\caption[\titlecap{Fuzzing a request for the Ruby backend}]{Fuzzing a request for the Ruby backend, the payload can be seen inside the address bar.}
%% 	\label{fig:postmanruby}
%% \end{figure}

%% \begin{figure}[!htbp]
%% 	\centering
%% 	\includegraphics[width=\linewidth]{System/EMI_Mailcatcher_Ruby}
%% 	\caption[\titlecap{\Email Header Injection proof of concept - Ruby}]{\Email header injection proof of concept - Ruby, we can see that multiple headers (bcc, x-check, subject) have been inserted into the resulting \email.}
%% 	\label{fig:mailcatcherruby}
%% \end{figure}

>>>>

The front-end for each of the three applications is shown in Listing~\ref{code:html}. The server-side code for PHP, Python, and Ruby is shown in Listings~\ref{code:phpemi}, \ref{code:pyemi}, and \ref{code:rubyemi} respectively.

% Adam: I think it might be nice to have the Ruby code here too. - DONE.

Before performing a wide scan of the web, we verified that our system was able to detect the \ehi vulnerabilities present in all the sample web applications.

@@

\begin{lstlisting}[language=HTML,caption={HTML page for showcasing
      \ehi, a simple front-end for our
      examples.},label={code:html}, float]
<!doctype html>
<html lang="en">
<head>
<meta charset="utf-8">
<meta name="author" content="XYZ">
<title>Mock Email</title>
</head>
<body>
<form action="{path-to-back-end}" method="post">
<input type="text" placeholder="Email" name="email" id="\email"><br>
<textarea name="msg" rows="20" cols="120"></textarea>
<input type="submit" value="Email Me!">
</form>
</body>
</html>
\end{lstlisting}
\input{Background/ruby}

%% \begin{figure}[tbp]
%% 	\centering
%% 	\includegraphics[width=\linewidth]{System/EMI_Postman_Ruby}
%% 	\caption[\titlecap{Fuzzing a request for the Ruby backend}]{Fuzzing a request for the Ruby backend, the payload can be seen inside the address bar.}
%% 	\label{fig:postmanruby}
%% \end{figure}

%% \begin{figure}[tbp]
%% 	\centering
%% 	\includegraphics[width=\linewidth]{System/EMI_Mailcatcher_Ruby}
%% 	\caption[\titlecap{\Email Header Injection proof of concept - Ruby}]{\Email header injection proof of concept - Ruby, we can see that multiple headers (bcc, x-check, subject) have been inserted into the resulting \email.}
%% 	\label{fig:mailcatcherruby}
%% \end{figure}
